---
title: "rfishbase-models"
output: 
  html_document: 
    keep_md: yes
---

Load packages
```{r warnings = FALSE}
library(devtools)
library(rfishbase)
library(ggplot2)
library(plyr)
suppressPackageStartupMessages(library(dplyr))
library(knitr)
library(tidyr)
library(readr)
library(ggthemes)
library(MuMIn)
library(visreg)
```

Load the data
```{r}
fb.all <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/fb.all.csv")
length(unique(fb.all$species))
names(fb.all)
temps.fb <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/temps.fb.csv")
temps.fb <- select(temps.fb, -SpecCode)
temps.fb <- temps.fb %>% 
  dplyr::rename(species = sciname) %>% 
  mutate(species = as.factor(species))
fb.temps <- inner_join(fb.all, temps.fb, by = "species")
names(fb.temps)
str(fb.temps)
ntbl <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/ntbl.csv")
table(fb.all$Herbivory2)
```

```{r}
?MuMIn
options(na.action = "na.fail")
fb.all <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/fb.all.csv")
fb.all <- fb.all %>% filter(!is.na(CA_mg),
                            !is.na(max_size),
                            !is.na(DemersPelag),
                            !is.na(TL),
                            !is.na(Habitat),
                            !is.na(FoodTroph.x),
                            !is.na(Herbivory2),
                            !is.na(taxon),
                            !is.na(Abs_lat))
length(unique(fb.all$species))

fb.all <- fb.all %>% 
  filter(!is.na(ZN_mg),
         !is.na(max_size), 
         !is.na(DemersPelag),
         !is.na(TL),
         !is.na(Habitat),
         !is.na(FoodTroph.x),
         !is.na(taxon),
         !is.na(Abs_lat))
summary(fb.all$CA_mg)

### this model contains all the traits I'm considering: body size, ocean zone use (DemersPelag), trophic level, habitat (marine/freshwater), trophic level of diet, herbivory, 
ZN.all <- lm(log(ZN_mg) ~ max_length + DemersPelag + TL + Habitat + FoodTroph.x + Herbivory2, data = fb.all)
CA.all <- lm(log(CA_mg) ~ max_length + DemersPelag + TL + Habitat + FoodTroph.x + Herbivory2, data = fb.all)

summary(CA.all)

dd <- dredge(CA.all, m.lim = c(NA, 1), extra = list(
    "R^2", "*" = function(x) {
        s <- summary(x)
        c(Rsq = s$r.squared, adjRsq = s$adj.r.squared,
            F = s$fstatistic[[1]])
    })
)

dd

subset(dd, delta < 4)
par(mar = c(3,5,6,4))
plot(dd, labAsExpr = TRUE)

model.sel(dd)

# Model average models with delta AICc < 4
model.avg(dd, subset = delta < 4)

#or as a 95% confidence set:
model.avg(dd, subset = cumsum(weight) <= .95) # get averaged coefficients

#'Best' model
summary(get.models(dd, 1)[[1]])


#### Calcium models ####
CA_old <- read_csv("/Users/Joey/Desktop/Nutrient_databases/nutmassCA_Feb24.csv")
CA_old2 <- read_csv("/Users/Joey/Desktop/Nutrient_databases/nut_sept22_lwr_dec3.csv")
CA_old3 <- read.csv("/Users/Joey/Desktop/Nutrient_databases/nut_mass_feb10_ff.csv")
ntbl <- read.csv("/Users/Joey/Documents/Nutrient_Analysis/data/ntbl.csv")

options(na.action = "na.omit")
CA.lat <- lm(log(CA_mg) ~ Abs_lat, data = fb.all)
CA.size1 <- lm(log(CA_mg) ~ Length, data = fb.all)
CA.size2 <- lm(log(CA_mg) ~ max_length, data = fb.all)
CA.size3 <- lm(log(CA_mg) ~ log(max_size), data = ntbl)
summary(CA.size1)

fb.CA.temps <- fb.temps %>%
  group_by(species) %>% 
    summarise(mean.CA = mean(CA_mg, na.rm = TRUE),
              mean.temp = mean(TempMin, na.rm = TRUE))

  
CA.temp <- lm(log(mean.CA) ~ mean.temp, data = fb.CA.temps)
visreg(CA.lat, xvar = "Abs_lat")
visreg(CA.size3, xvar = "max_size", xtrans = log)
visreg(CA.temp, xvar = "mean.temp")
summary(CA.temp)
?visreg
length(unique(fb.all$species))

#### merge FB and SLB basic info ####
intbl.basic <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/intbl.basic.csv")
fb.length <- fb.all %>% 
  select(species, CA_mg, ZN_mg, FE_mg, EPA_g, DHA_g, Length, max_length, Subgroup, Habitat) %>% filter(Habitat != "brackish")

slb.length <- intbl.basic %>% 
  select(species, CA_mg, ZN_mg, FE_mg, EPA_g, DHA_g, Length, max_length, Subgroup, Habitat)

length.CA <- dplyr::bind_rows(fb.length, slb.length)
CA.length <- lm(log(CA_mg) ~ log(Length), data = length.CA) 
summary(CA.length)
visreg(CA.length, xvar = "Length", xtrans = log)
ggplot(length.CA, aes(x = Length, y = log(DHA_g), color = Subgroup, shape = Habitat)) + stat_summary(fun.y= "mean", geom = "point") + scale_x_log10() + geom_smooth(method = 'lm')

#### inverts ecology ####
intbl.all <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/intbl.all.csv")

length(unique(intbl.all$species))
CA.inverts <- lm(log(FE_mg.x) ~ log(Length) + FoodTroph + Subgroup.x, data = intbl.all)

CA.inverts.size <- lm(log(FE_mg.x) ~ log(Length), data = intbl.all)
visreg(CA.inverts.size, xvar = "Length", xtrans = log)
visreg(CA.inverts, xvar = "Length", xtrans = log)
summary(CA.inverts.size)
summary(CA.inverts)
