---
title: "rfishbase-models"
output: 
  html_document: 
    keep_md: yes
---

Load packages
```{r warnings = FALSE}
library(devtools)
library(rfishbase)
library(ggplot2)
library(plyr)
suppressPackageStartupMessages(library(dplyr))
library(knitr)
library(tidyr)
library(readr)
library(ggthemes)
library(MuMIn)
library(visreg)
library(broom)
```

Load the data
```{r}


temps.fb <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/temps.fb.csv")
temps.fb <- select(temps.fb, -SpecCode)
temps.fb <- temps.fb %>% 
  dplyr::rename(species = sciname) %>% 
  mutate(species = as.factor(species))
fb.temps <- inner_join(fb.all, temps.fb, by = "species")


```


```{r}
#### merge FB and SLB basic info ####
intbl.basic <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/intbl.basic.csv")
intbl.all <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/intbl.all.csv")
fb.all <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/fb.all.csv")
ntbl <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/ntbl.csv")

fb.length <- fb.all %>% 
   dplyr::select(species, CA_mg, ZN_mg, FE_mg, EPA_g, DHA_g, Length, max_length, Subgroup, Habitat, TL, FoodTroph.x, Herbivory2, Abs_lat, DemersPelag, taxon, max_size) %>% 
  rename(FoodTroph = FoodTroph.x) %>% 
  mutate(species = as.factor(species))

slb.length <- intbl.all %>% 
   dplyr::select(species, CA_mg.x, ZN_mg.x, FE_mg.x, EPA_g.x, DHA_g.x, Length, max_length.x, Subgroup.x, Habitat.x, TL.x, FoodTroph, Herbivory2, Abs_lat.x, DemersPelag, taxon.x, max_size.x)

slb.length <- slb.length %>% 
 rename(CA_mg = CA_mg.x,
         ZN_mg = ZN_mg.x,
         FE_mg = FE_mg.x, 
         EPA_g = EPA_g.x, 
         DHA_g = DHA_g.x,
        Length = Length,
         max_length = max_length.x,
         Subgroup = Subgroup.x, 
         Habitat = Habitat.x,
         TL = TL.x,
        FoodTroph = FoodTroph,
        Herbivory2 = Herbivory2,
        DemersPelag = DemersPelag,
         Abs_lat = Abs_lat.x,
         taxon = taxon.x,
        max_size = max_size.x) %>% 
  mutate(species = as.factor(species))

slb.length$species <- as.factor(slb.length$species)
slb.length$Subgroup <- as.factor(slb.length$Subgroup)
slb.length$DemersPelag <- as.factor(slb.length$DemersPelag)
slb.length$Habitat <- as.factor(slb.length$Habitat)
slb.length$Herbivory2 <- as.factor(slb.length$Herbivory2)
slb.length$taxon <- as.factor(slb.length$taxon)


all.n <- dplyr::bind_rows(fb.length, slb.length) %>% 
  mutate(Subgroup = as.factor(Subgroup),
         taxon = as.factor(taxon), 
         DemersPelag = as.factor(DemersPelag),
         Herbivory2 = as.factor(Herbivory2),
         Habitat = as.factor(Habitat))

all.n$species <- as.factor(all.n$species)
all.n$Subgroup <- as.factor(all.n$Subgroup)
all.n$DemersPelag <- as.factor(all.n$DemersPelag)
all.n$Habitat <- as.factor(all.n$Habitat)
all.n$Herbivory2 <- as.factor(all.n$Herbivory2)
all.n$taxon <- as.factor(all.n$taxon)

write_csv(all.n, "/Users/Joey/Documents/Nutrient_Analysis/data/all.n.csv")
all.n <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/all.n.csv")
read_csv()
?read_csv


#### Create nutrient-specific datasets without missing values ####
all.CA <- all.n %>% 
  filter(!is.na(CA_mg),
         !is.na(DemersPelag),
         !is.na(TL),
         !is.na(Habitat),
         !is.na(FoodTroph),
         !is.na(Herbivory2),
         !is.na(taxon),
         !is.na(Abs_lat),
         !is.na(Subgroup),
         !is.na(max_size))

fb.all.ZN <- all.n %>% 
  filter(!is.na(ZN_mg),
         !is.na(Length), 
         !is.na(DemersPelag),
         !is.na(TL),
         !is.na(Habitat),
         !is.na(FoodTroph),
         !is.na(taxon),
         !is.na(Abs_lat))

slb.ZN <- slb.length %>% 
   filter(!is.na(ZN_mg),
         !is.na(Length), 
         !is.na(DemersPelag),
         !is.na(TL),
         !is.na(Habitat),
         !is.na(FoodTroph),
         !is.na(taxon),
         !is.na(Abs_lat))
str(slb.ZN)

fb.all.FE <- all.n %>% 
  filter(!is.na(FE_mg),
         !is.na(Length), 
         !is.na(DemersPelag),
         !is.na(TL),
         !is.na(Habitat),
         !is.na(FoodTroph),
         !is.na(taxon),
         !is.na(Abs_lat),
         !is.na(Subgroup))

fb.all.EPA <- all.n %>% 
  filter(!is.na(EPA_g),
         !is.na(Length), 
         !is.na(DemersPelag),
         !is.na(TL),
         !is.na(Habitat),
         !is.na(FoodTroph),
         !is.na(taxon),
         !is.na(Abs_lat),
         !is.na(Subgroup))
fb.all.DHA <- all.n %>% 
  filter(!is.na(DHA_g),
         !is.na(Length), 
         !is.na(DemersPelag),
         !is.na(TL),
         !is.na(Habitat),
         !is.na(FoodTroph),
         !is.na(taxon),
         !is.na(Abs_lat),
         !is.na(Subgroup))


str(fb.all.DHA)

### this model contains all the traits I'm considering: body size, ocean zone use (DemersPelag), trophic level, habitat (marine/freshwater), trophic level of diet, herbivory, 

#### Zinc ####

table(fb.all.ZN$Subgroup)
ZN.slb <- lm(log(ZN_mg) ~ log(Length) + DemersPelag + Abs_lat, data = slb.ZN, na.action = "na.omit")
ZN.slb.length <- lm(log(ZN_mg) ~ log(Length), data = slb.length, na.action = "na.omit")
ZN.all <- (lm(log(ZN_mg) ~ log(Length) + DemersPelag + TL + Habitat + FoodTroph + Abs_lat, data = fb.all.ZN, na.action = "na.omit"))
summary(ZN.slb, conf.int = TRUE)
kable(tidy(ZN.all))
alias(ZN.slb)
test.ZN.slb <- tidy(ZN.slb, conf.int =TRUE)
test.ZN.slb$term <- factor(test.ZN.slb$term, levels=unique(test.ZN.slb$term))
ggplot(test.ZN.slb, aes(x=term, y=estimate, ymin=conf.low, ymax=conf.high)) +
  geom_pointrange() + 
  coord_flip() + 
  geom_hline(aes(x=0), lty=2) +
  xlab('term ZN') +
  ylab('Regression Coefficient') + theme(legend.position="none")

hist(slb.ZN$ZN_mg)


summary(fb.all.ZN$ZN_mg)
summary(all.n$ZN_mg)

ddZ <- dredge(ZN.all, m.lim = c(NA, 1), extra = list(
    "R^2", "*" = function(x) {
        s <- summary(x)
        c(Rsq = s$r.squared, adjRsq = s$adj.r.squared,
            F = s$fstatistic[[1]])
    })
)
model.sel(ddZ)
subset(ddZ, delta < 4)
par(mar = c(3,5,6,4))
plot(ddZ, labAsExpr = TRUE)

# Model average models with delta AICc < 4
model.avg(ddZ, subset = delta < 4)

#or as a 95% confidence set:
model.avg(dd, subset = cumsum(weight) <= .95) # get averaged coefficients

#'Best' model
summary(get.models(ddZ, 1)[[1]])

## so the results for zinc are that taxon is the most important predictor, taxon alone explains 36% of the variation. It is the only term retained in the top model set. 

ggplot(all.n, aes(x = Length, y = log(ZN_mg), color = Subgroup, shape = Habitat)) + stat_summary(fun.y= "mean", geom = "point") + scale_x_log10() + geom_smooth(method = 'lm')
ggplot(all.n, aes(x = Length, y = log(ZN_mg))) + stat_summary(fun.y= "mean", geom = "point") + scale_x_log10() + geom_smooth(method = 'lm')

zinc.l <- lm(log(ZN_mg) ~ log(Length), data = all.n) %>% tidy(., conf.int = TRUE)
zinc.l <- lm(log(ZN_mg) ~ log(Length), data = fb.all.ZN)
summary(zinc.l)
visreg(zinc.l, xvar = "Length", by = "Subgroup", overlay = FALSE, xtrans =  log)
ggsave("zn.length.all.png")


#### Iron ####
str(fb.all.FE)

fb.all.FE <- fb.all.FE %>% filter(taxon != "Crabs, sea-spiders", 
                                  taxon != "Lobsters, spiny-rock lobsters") %>% 
  droplevels(.)

levels(fb.all.FE$taxon)
?alias

FE.all <- standardize(lm(log(FE_mg) ~ log(Length) + DemersPelag + TL + Habitat + FoodTroph+ Herbivory2, data = fb.all.FE, na.action = "na.omit"))
test.FE <- tidy(FE.all, conf.int =TRUE)
test.FE$term <- factor(test.FE$term, levels=unique(test.FE$term))
ggplot(test.FE, aes(x=term, y=estimate, ymin=conf.low, ymax=conf.high)) +
  geom_pointrange() + 
  coord_flip() + 
  geom_hline(aes(x=0), lty=2) +
  xlab('term FE') +
  ylab('Regression Coefficient') + theme(legend.position="none")


View(alias(FE.all))
confint(FE.all)
summary(FE.all, conf.int = TRUE)
kable(tidy(FE.all))


ddF <- dredge(FE.all, m.lim = c(NA, 1), extra = list(
    "R^2", "*" = function(x) {
        s <- summary(x)
        c(Rsq = s$r.squared, adjRsq = s$adj.r.squared,
            F = s$fstatistic[[1]])
    })
)
model.sel(ddF)
subset(ddF, delta < 4)
par(mar = c(3,5,6,4))
plot(ddF, labAsExpr = TRUE)

# Model average models with delta AICc < 4
model.avg(ddF, subset = delta < 4)

#or as a 95% confidence set:
model.avg(ddF, subset = cumsum(weight) <= .95) # get averaged coefficients

#'Best' model
summary(get.models(ddF, 1)[[1]])

ggplot(all.n, aes(x = Length, y = log(FE_mg), color = Subgroup, shape = Habitat)) + stat_summary(fun.y= "mean", geom = "point") + scale_x_log10() + geom_smooth(method = 'lm')
ggplot(fb.all.FE, aes(x = Length, y = log(FE_mg))) + stat_summary(fun.y= "mean", geom = "point") + scale_x_log10() + geom_smooth(method = 'lm')

#### Calcium ####
all.CA <- all.n %>% 
  filter(!is.na(CA_mg),
         !is.na(DemersPelag),
         !is.na(TL),
         !is.na(Habitat),
         !is.na(FoodTroph),
         !is.na(Herbivory2),
         !is.na(taxon),
         !is.na(Abs_lat),
         !is.na(Subgroup),
         !is.na(max_size))

summary(slb.length$FE_mg)

inverts.new <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/aquatic_inverts_micronutrients.csv")

inverts.new$length.reported_cm <- as.numeric(inverts.new$length.reported_cm)

hist(inverts.new$length.reported_cm)



CA.new <- lm(log(CA_mg) ~ length.reported_cm, data = inverts.new)
summary(CA.new)
str(inverts.new)
visreg(CA.new, xvar = "length.reported_cm")

CA.all <- standardize(lm(log(CA_mg) ~ log(Length) + DemersPelag + TL + FoodTroph + Herbivory2 + Habitat + Abs_lat, data = all.CA, na.action = "na.omit"))

all.CA.finfish <- all.n %>% 
  filter(Subgroup == "Finfish")
CA.all <- standardize(lm(log(CA_mg) ~ log(max_size_g) + TL + Habitat + Abs_lat, data = all.CA.finfish))

summary(log(all.CA.finfish$max_size_g))
all.CA.finfish <- all.CA.finfish %>% 
  mutate(max_size_g = max_size * 1000)

summary(CA.all, conf.int = TRUE)
kable(tidy(CA.all, conf.int =TRUE))
test.CA <- tidy(CA.all, conf.int =TRUE)
test.CA$term <- factor(test.CA$term, levels=unique(test.CA$term))
ggplot(test.CA, aes(x=term, y=estimate, ymin=conf.low, ymax=conf.high)) +
  geom_pointrange() + 
  coord_flip() + 
  geom_hline(aes(x=0), lty=2) +
  xlab('term CA') +
  ylab('Regression Coefficient') + theme(legend.position="none")

ddC <- dredge(CA.all, m.lim = c(NA, 1), extra = list(
    "R^2", "*" = function(x) {
        s <- summary(x)
        c(Rsq = s$r.squared, adjRsq = s$adj.r.squared,
            F = s$fstatistic[[1]])
    })
)
model.sel(ddC)
subset(ddC, delta < 4)
par(mar = c(3,5,6,4))
plot(ddC, labAsExpr = TRUE)

# Model average models with delta AICc < 4
model.avg(ddC, subset = delta < 4)

#or as a 95% confidence set:
model.avg(ddC, subset = cumsum(weight) <= .95) # get averaged coefficients

#'Best' model
summary(get.models(ddC, 1)[[1]])

#### EPA ####
EPA.all <- standardize(lm(log(EPA_g) ~ log(Length) + DemersPelag + TL + Habitat + FoodTroph + Herbivory2 + Abs_lat, data = fb.all.EPA, na.action = "na.omit"))
summary(EPA.all, conf.int = TRUE)
kable(tidy(EPA.all, conf.int = TRUE))
test <- tidy(EPA.all, conf.int = TRUE)
test$term <- factor(test$term, levels=unique(test$term))
ggplot(test, aes(x=term, y=estimate, ymin=conf.low, ymax=conf.high)) +
  geom_pointrange() + 
  coord_flip() + 
  geom_hline(aes(x=0), lty=2) +
  xlab('term EPA') +
  ylab('Regression Coefficient') + theme(legend.position="none")

ddE <- dredge(EPA.all, m.lim = c(NA, 1), extra = list(
    "R^2", "*" = function(x) {
        s <- summary(x)
        c(Rsq = s$r.squared, adjRsq = s$adj.r.squared,
            F = s$fstatistic[[1]])
    })
)
model.sel(ddE)
subset(ddE, delta < 4)
par(mar = c(3,5,6,4))
plot(ddE, labAsExpr = TRUE)

# Model average models with delta AICc < 4
model.avg(ddE, subset = delta < 4)

#or as a 95% confidence set:
model.avg(ddE, subset = cumsum(weight) <= .95) # get averaged coefficients

#'Best' model
summary(get.models(ddE, 1)[[1]])

#### DHA ####
install.packages("arm")
library(arm)
DHA.all <- standardize(lm(log(DHA_g) ~ log(Length) + DemersPelag + TL + Habitat + FoodTroph + Herbivory2 + Abs_lat, data = fb.all.DHA, na.action = "na.omit"))
summary(DHA.all, conf.int = TRUE)
kable(tidy(DHA.all, conf.int = TRUE))
test <- tidy(DHA.all, conf.int = TRUE)

test$term <- factor(test$term, levels=unique(test$term))
ggplot(test, aes(x=term, y=estimate, ymin=conf.low, ymax=conf.high)) +
  geom_pointrange() + 
  coord_flip() + 
  geom_hline(aes(x=0), lty=2) +
  xlab('term DHA') +
  ylab('Regression Coefficient') + theme(legend.position="none")



ddD <- dredge(DHA.all, m.lim = c(NA, 1), extra = list(
    "R^2", "*" = function(x) {
        s <- summary(x)
        c(Rsq = s$r.squared, adjRsq = s$adj.r.squared,
            F = s$fstatistic[[1]])
    })
)
model.sel(ddD)
subset(ddD, delta < 4)
par(mar = c(3,5,6,4))
plot(ddD, labAsExpr = TRUE)

# Model average models with delta AICc < 4
model.avg(ddD, subset = delta < 4)

#or as a 95% confidence set:
model.avg(ddD, subset = cumsum(weight) <= .95) # get averaged coefficients

#'Best' model
summary(get.models(ddD, 1)[[1]])


#### inverts ecology ####
intbl.all <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/intbl.all.csv")

length(unique(intbl.all$species))
CA.inverts <- lm(log(FE_mg.x) ~ log(Length) + FoodTroph + Subgroup.x, data = intbl.all)

CA.inverts.size <- lm(log(ZN_mg.x) ~ log(Length) + FoodTroph, data = intbl.all)
visreg(CA.inverts.size, xvar = "FoodTroph")
visreg(CA.inverts, xvar = "Length", xtrans = log)
summary(CA.inverts.size)
summary(CA.inverts)
