---
title: "Homework3"
output: 
  html_document: 
    keep_md: yes
---

Initial set up
```{r}
library(plotrix)
library(ggthemes)
library(dplyr)
library(ggplot2)
library(knitr)
library(Hmisc)

nut <- read.csv("~/Desktop/Nutrient_databases/nut_sept22_lwr_dec3.csv", comment.char="#", stringsAsFactors=FALSE)

ntbl <- tbl_df(nut)

glimpse(ntbl)
```

Change variable names to more intuitive names
```{r}
 ntbl <- ntbl %>%
  rename(species = ASFIS.Scientific.name,
         taxon = ISSCAAP_cat,
         max_length = SLMAX)
```

Pull out variables we will use in this analysis
```{r select variables of interest}
ntbl <- ntbl %>%
  select(species, taxon, max_length, TL, CA_mg, EPA_g, DHA_g, ZN_mg, HG_mcg, lwA, lwB, Habitat, Subgroup, Abs_lat)
```

Convert max length to max body size using length-weight conversion (W = a × L^b)
```{r}
ntbl <- ntbl %>%
  mutate(max_size = lwA * (max_length^lwB))
ntbl %>%
  glimpse()
```

What if we want to know the number of species in each habitat?
```{r}
n_obs_hab <- ntbl %>%
  group_by(Habitat) %>%
  tally
knitr::kable(n_obs_hab, align = 'c', format = 'markdown')
```


How does body size vary by habitat?
```{r}
hab.size <- ntbl %>%
  filter(Habitat %in% c("marine", "freshwater", "brackish")) %>%
  filter(!is.na(max_size)) %>% 
  group_by(Habitat) %>%
  summarise_each(funs(mean, median, std.error), max_size)
knitr::kable(hab.size, align = 'c', format = 'markdown')

```

How does body size vary by taxon?
```{r}
taxon.size <- ntbl %>%
  filter(Habitat %in% c("marine", "freshwater", "brackish")) %>%
  filter(!is.na(max_size)) %>% 
  group_by(taxon) %>%
  summarise_each(funs(mean, median), max_size)
knitr::kable(taxon.size, align = 'c', format = 'markdown')

```

```{r}
ntbl %>%
  filter(!is.na(CA_mg)) %>%
  filter(Habitat == "marine") %>%
  group_by(taxon) %>%
  summarise_each(funs(min, max, mean), CA_mg)
```

How does calcium vary with body size?
```{r body size CA by hab, cal.size}
ggplot(subset(ntbl, Habitat %in% c("marine", "freshwater")), aes(x=max_size, y=CA_mg, group = Habitat, color = Habitat)) + stat_summary(fun.y= "mean", geom = "point") + geom_hline(aes(yintercept=250)) + stat_smooth(method = "lm") + theme_pander() + scale_x_log10() + scale_y_log10()
```

How many species in the dataset have 50% of RDI for EPA in one portion?
```{r EPA RDI}
EPA.RDI <- ntbl %>%
  filter(EPA_g > 0.5) %>% 
group_by(taxon) %>%
  tally

EPA.RDI.prop <- EPA.RDI %>% mutate (RDI.prop = (n/45)*100)
knitr::kable(EPA.RDI.prop, align = 'c', format = 'markdown')

EPA.total <- ntbl %>%
filter(!is.na(EPA_g)) %>% 
  group_by(taxon) %>%
  tally
knitr::kable(EPA.total, align = 'c', format = 'markdown')
```
