---
title: "Homework3"
output: 
  html_document: 
    keep_md: yes
    toc: yes
---


```{r}
library(plotrix)
library(ggthemes)
library(dplyr)
library(ggplot2)
library(knitr)
library(Hmisc)

nut <- read.csv("~/Desktop/Nutrient_databases/nut_sept22_lwr_dec3.csv", comment.char="#", stringsAsFactors=FALSE)

str(nut)
summary(nut)

ntbl <- tbl_df(nut)

glimpse(ntbl)

```

Change variable names to more intuitive names
```{r}
 ntbl <- ntbl %>%
  rename(species = ASFIS.Scientific.name,
         taxon = ISSCAAP_cat,
         max_length = SLMAX)
```

Pull out variables we will use in this analysis
```{r select variables of interest}
ntbl <- ntbl %>%
  select(species, taxon, max_length, TL, CA_mg, EPA_g, DHA_g, ZN_mg, HG_mcg, lwA, lwB, Habitat, Subgroup, Abs_lat)
```

Convert max length to max body size using length-weight conversion (W = a × L^b)
```{r}
ntbl <- ntbl %>%
  mutate(max_size = lwA * (max_length^lwB))
ntbl %>%
  glimpse()
```

How many observations are there per habitat?
```{r}
ntbl %>%
  group_by(Habitat) %>%
  summarize(n_obs = n())
```

```{r}
ntbl %>%
  group_by(Habitat) %>%
  tally
```

What if we want to know the number of species in each habitat?
```{r}
mean.size <- ntbl %>%
  filter(Habitat %in% c("marine", "freshwater", "brackish")) %>%
  filter(!is.na(max_size)) %>% 
  group_by(Habitat) %>%
  summarise_each(funs(mean, median, std.error), max_size)
knitr::kable(mean.size)


taxon.size <- ntbl %>%
  filter(Habitat %in% c("marine", "freshwater", "brackish")) %>%
  filter(!is.na(max_size)) %>% 
  group_by(taxon) %>%
  summarise_each(funs(mean, median), max_size/1000)
knitr::kable(taxon.size)
```
```{r min and max}
calcium <- ntbl %>%
  filter(!is.na(CA_mg)) %>%
  filter(Habitat == "marine") %>%
  group_by(taxon) %>%
  summarise_each(funs(min, max, mean), CA_mg)
knitr::kable(calcium)

zinc <- ntbl %>%
  filter(!is.na(ZN_mg) | !is.na(CA_mg)) %>%
  filter(Habitat == "marine") %>%
  group_by(taxon) %>%
  summarise_each(funs(min, max, mean), ZN_mg, CA_mg)
knitr::kable(zinc)

```

```{r trimmed mean}
stat_sum_single <- function(fun, geom="point", colour = "red", ...) {
  stat_summary(fun.y=fun, colour=colour, geom=geom, size = 3, ...)
}

ggplot(ntbl, aes(x=factor(Habitat), y=max_size, group = 1)) +
  stat_sum_single(mean, trim = 0.30, colour = "purple") + 
  stat_sum_single(mean, trim = 0.05, colour = "blue")

stat_sum_single <- function(fun, geom="point", colour = "red", ...) {
  stat_summary(fun.y=fun, colour=colour, geom=geom, size = 3, ...)
}

ggplot(ntbl, aes(x=factor(taxon), y=log(max_size), group = 1)) +
  stat_sum_single(mean, trim = 0.30, colour = "purple") + 
  stat_sum_single(mean, trim = 0.05, colour = "blue") +
  stat_summary(fun.data = mean_cl_boot, geom = "pointrange") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme_pander()
 




```
```{r body size CA by hab}
p <- ggplot(subset(ntbl, Habitat %in% c("marine", "freshwater")), aes(x=log(max_size), y=log(CA_mg), color = Habitat))
p + geom_point()
p + stat_summary(aes(y = log(CA_mg)), fun.y=mean, geom = "point") + geom_hline(aes(yintercept=log(250))) + stat_smooth(method = "lm") + theme_pander()
```


```{r}
ggplot(ntbl, aes(x = max_size, y = CA_mg, color = Habitat)) + geom_point() +
  scale_x_log10()

ggplot(ntbl, aes(x = log(max_size), y = log(EPA_g), color = Habitat)) + geom_point()

p <- ggplot(subset(ntbl, Habitat == "marine"), aes(x=Abs_lat, y=log(EPA_g)))
p + geom_point()
p + stat_summary(aes(y = log(EPA_g)), fun.y=mean, geom = "point") + geom_hline(aes(yintercept=log(0.5))) + stat_smooth(method = "lm") + theme_pander()



p <- ggplot(subset(ntbl, Habitat == "marine"), aes(x=log(max_size), y=log(EPA_g)))
p + geom_point()
p + stat_summary(aes(y = log(EPA_g)), fun.y=mean, geom = "point") + geom_hline(aes(yintercept=log(0.25)))
             
```

How does calcium content vary with body size?
```{r calcium body size}
p <- ggplot(subset(ntbl, Habitat == "freshwater"), aes(x=log(max_size), y=log(CA_mg)))
p + geom_point()
p + stat_summary(aes(y = log(CA_mg)), fun.y=mean, geom = "point") + geom_hline(aes(yintercept=log(250))) + stat_smooth(method = "lm") + theme_pander()

```

How many species in the dataset have 50% of RDI for EPA in one portion?
```{r EPA RDI}
EPA.RDI <- ntbl %>%
  filter(EPA_g > 0.5) %>% 
group_by(taxon) %>%
  tally
knitr::kable(EPA.RDI)
```

