---
title: "nutrient_results"
output: 
  html_document: 
    keep_md: yes
    toc: yes
---

#### Script for the results section of the Nutritional diversity paper


```{r include=FALSE}
knitr::opts_chunk$set(
  comment = "# ",
  error = FALSE,
  cache = TRUE,
  message = FALSE,
  warning = FALSE
)
```


Load packages and data
```{r}
library(arm)
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(vegan))
library(readr)
library(ggplot2)
library(tidyr)
library(ggthemes)
library(knitr)
library(broom)
library(coefplot)

ntbl <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/ntbl2.csv")
n.long <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/ntbl.long.csv")
n.long <- read.csv("/Users/Joey/Documents/Nutrient_Analysis/data/aq.long.csv")
```


#### Result 1. There is considerable variability in nutritional profile among aquatic taxa.

```{r}
# facetted histograms for the nutrient ranges
g <- ggplot(n.long, aes(concentration)) + geom_histogram(binwidth = 0.07)
g + facet_grid(nutrient ~ ., scales = "free_y") + theme_bw() + scale_x_log10()


n.micro <- n.long %>% 
  filter(nutrient %in% c("CA_mg", "ZN_mg", "FE_mg", "DHA_g", "EPA_g")) 

#now just for micronutrients
g <- ggplot(n.micro, aes(concentration)) + geom_histogram(binwidth = 0.07)
g + facet_grid(nutrient ~ ., scales = "free_y") + theme_bw() + scale_x_log10()
ggsave("/Users/Joey/Documents/Nutrient_Analysis/figures/nut-hist.png")

#an alternative
ggplot(n.micro, aes(x = concentration, fill=nutrient)) + geom_density(alpha=.3) + scale_x_log10()

```

Find the min and max for each nutrient.

Calcium 
```{r}
hist(log(ntbl$CA_mg))
hist(ntbl$CA_mg)
summary(ntbl$CA_mg)
length(!is.na(ntbl$CA_mg))

ggplot(ntbl, aes(CA_mg)) + geom_histogram()

#" How many species do we have calcium data for? 99 species.
ntbl %>% 
  filter(!is.na(CA_mg)) %>% 
  distinct(species) %>%
  count()

#' average by taxon
ntbl %>% 
  filter(!is.na(CA_mg)) %>% 
  group_by(taxon) %>% 
  summarise(mean.CA = mean(CA_mg),
            n = n_distinct(species)) %>% 
  arrange(desc(mean.CA)) %>%
  knitr::kable(., align = 'c', format = 'markdown', digits = 2)
```

Zinc
```{r}
hist(ntbl$ZN_mg)
summary(ntbl$ZN_mg)
length(!is.na(ntbl$ZN_mg))

#" How many species do we have zinc data for? 101 species.
ntbl %>% 
  filter(!is.na(ZN_mg)) %>% 
  distinct(species) %>%
  count()

#' average by taxon
ntbl %>% 
  filter(!is.na(ZN_mg)) %>% 
  group_by(taxon) %>% 
  summarise(mean.ZN = mean(ZN_mg),
            n = n_distinct(species)) %>% 
  arrange(desc(mean.ZN)) %>%
  knitr::kable(., align = 'c', format = 'markdown', digits = 2)
```

Iron
```{r}
hist(ntbl$FE_mg)
summary(ntbl$FE_mg)


#" How many species do we have iron data for? 101 species.
ntbl %>% 
  filter(!is.na(FE_mg)) %>% 
  distinct(species) %>%
  count()

#' average by taxon
ntbl %>% 
  filter(!is.na(FE_mg)) %>% 
  group_by(taxon) %>% 
  summarise(mean.FE = mean(FE_mg),
            n = n_distinct(species)) %>% 
  arrange(desc(mean.FE)) %>%
  knitr::kable(., align = 'c', format = 'markdown', digits = 2)
```

#### EPA ####
```{r}
hist(ntbl$EPA_g)
summary(ntbl$EPA_g)


#" How many species do we have EPA data for? 238 species.
ntbl %>% 
  filter(!is.na(EPA_g)) %>% 
  distinct(species) %>%
  count()

#' average by taxon
ntbl %>% 
  filter(!is.na(EPA_g)) %>% 
  group_by(taxon) %>% 
  summarise(mean.EPA = mean(EPA_g),
            n = n_distinct(species)) %>% 
  arrange(desc(mean.EPA)) %>%
  knitr::kable(., align = 'c', format = 'markdown', digits = 2)
```

#### DHA
```{r}
hist(ntbl$DHA_g)
summary(ntbl$DHA_g)


#" How many species do we have DHA data for? 235 species.
ntbl %>% 
  filter(!is.na(DHA_g)) %>% 
  distinct(species) %>%
  count()

#' average by taxon
ntbl %>% 
  filter(!is.na(DHA_g)) %>% 
  group_by(taxon) %>% 
  summarise(mean.DHA = mean(DHA_g),
            n = n_distinct(species)) %>% 
  arrange(desc(mean.DHA)) %>%
  knitr::kable(., align = 'c', format = 'markdown', digits = 2)
``` 

#### Protein
```{r}
hist(ntbl$PROTEIN)
summary(ntbl$PROTEIN)


#" How many species do we have DHA data for? 235 species.
ntbl %>% 
  filter(!is.na(PROTEIN)) %>% 
  distinct(species) %>%
  count()

#' average by taxon
ntbl %>% 
  filter(!is.na(PROTEIN)) %>% 
  group_by(taxon) %>% 
  summarise(mean.protein = mean(PROTEIN),
            n = n_distinct(species)) %>% 
  arrange(desc(mean.protein)) %>%
  knitr::kable(., align = 'c', format = 'markdown', digits = 2)
``` 

#### Fat
```{r}
hist(ntbl$FAT)
summary(ntbl$FAT)


#" How many species do we have DHA data for? 235 species.
ntbl %>% 
  filter(!is.na(FAT)) %>% 
  distinct(species) %>%
  count()

#' average by taxon
ntbl %>% 
  filter(!is.na(FAT)) %>% 
  group_by(taxon) %>% 
  summarise(mean.FAT = mean(FAT),
            n = n_distinct(species)) %>% 
  arrange(desc(mean.FAT)) %>%
  knitr::kable(., align = 'c', format = 'markdown', digits = 2)
``` 

#### Result 2: Functional groups have distinct multi-nutrient profiles (mds plot with finfish/crustaceans/molluscs color coded).

```{r}
ntbl.raw <- read.csv("~/Documents/Nutrient_Analysis/data/ntbl2.csv")
inverts.new <- read.csv("~/Documents/Nutrient_Analysis/data/aquatic_inverts_micronutrients.csv")

ntbl.raw <- tbl_df(ntbl.raw)
```

What I did here was to run the same multivariate analysis using the new inverts data, just for CA, FE and ZN.
```{r}
ntbl.minerals <- ntbl.raw %>% 
  dplyr::select(Subgroup, species, CA_mg, FE_mg, ZN_mg)
```
```{r}
inverts.minerals <- inverts.new %>% 
  dplyr::select(Subgroup, species, CA_mg, FE_mg, ZN_mg) %>% 
  filter(Subgroup != "Echinoderm") 
```

```{r}
minerals <- bind_rows(ntbl.minerals, inverts.minerals)
minerals$Subgroup <- as.factor(minerals$Subgroup)
minerals$species <- as.factor(minerals$species)


min.mat <- minerals %>% 
  group_by(species) %>% 
  summarise(mean.CA = mean(CA_mg*1000, na.rm = TRUE),
            mean.ZN = mean(ZN_mg*1000, na.rm = TRUE), 
            mean.FE = mean(FE_mg*1000, na.rm = TRUE)) %>%
  filter(!is.na(mean.CA)) %>%
  filter(!is.na(mean.ZN)) %>%
  filter(!is.na(mean.FE)) 

matrix.min <- data.matrix(min.mat[, 2:4])
rownames(matrix.min) <- min.mat$species 
```
```{r}
names(minerals)

str(minerals)
min.taxon <- minerals %>% 
  dplyr::group_by(species) %>% 
  dplyr::select(Subgroup) %>% 
  distinct(species)

min.env <- semi_join(min.taxon, min.mat, by = "species")
rownames(min.env) <- min.env$species 
dim(min.env)
```
##### ordination
```{r}
ord.mine <- metaMDS(matrix.min, distance="bray", trymax=100)
ord.mine$stress
plot(ord.mine, type = "t",cex=.5)
site.scaling <- as.data.frame(ord.mine$points)
points(site.scaling,pch=16)


site.scaling$nfi_plot <- row.names(site.scaling)
min.env$nfi_plot <- row.names(min.env)

new.compiled <- merge(site.scaling, min.env, by=c("nfi_plot"))
new.compiled$Subgroup <- as.factor(new.compiled$Subgroup)
```

####now replot ordination, with groups colour-coded##
```{r}
plot(ord.mine, type = "n", cex=1)
points(new.compiled$MDS1, new.compiled$MDS2, pch= as.integer(new.compiled$Subgroup), cex = 1)
points(new.compiled$MDS1, new.compiled$MDS2, col = (as.integer(new.compiled$Subgroup)), pch= as.integer(new.compiled$Subgroup), cex = 1)

## add confidence ellipses around subgroups

ordiellipse(ord.mine, draw = "polygon", new.compiled$Subgroup, conf = 0.95, label = T)
ordihull(ord.mine, draw = "polygon", new.compiled$Subgroup, conf = 0.95, label = T)
# ordicluster(ord.mine, draw = "polygon", new.compiled$Subgroup, conf = 0.95, label = T)
ordispider(ord.mine, new.compiled$Subgroup,col="grey")
legend('topleft', legend = levels(new.compiled$Subgroup), col = 1:3, pch = 16, cex = 0.8)
```

calculate Bray-Curtis distance among samples
```{r}
comm.bc.dist <- vegdist(matrix.min, method = "bray")
hist(comm.bc.dist)

# cluster communities using average-linkage algorithm
comm.bc.clust <- hclust(comm.bc.dist, method = "average")

# plot cluster diagram
plot(comm.bc.clust, ylab = "Bray-Curtis dissimilarity")
```

Use betadisper to test the significance of the multivariate groups
```{r}
min.subgroup <- min.env$Subgroup
mod <- betadisper(comm.bc.dist, min.subgroup)

## Perform test
anova(mod)

## Permutation test for F
permutest(mod, pairwise = TRUE, permutations = 99)

## Tukey's Honest Significant Differences
(mod.HSD <- TukeyHSD(mod))
plot(mod.HSD)
boxplot(mod)

## Using group centroids
mod3 <- betadisper(comm.bc.dist, min.subgroup, bias.adjust = TRUE)
mod3
permutest(mod3, permutations = 99)
anova(mod3)
plot(mod3)
boxplot(mod3)
plot(TukeyHSD(mod3))
```

#### Use adonis to ask whether the group means in multivariate space are different from each other ####
```{r}
min.subgroup %>% 
  data_frame(subgrp = .) %>% 
  adonis(comm.bc.dist ~ subgrp, data = .)
```

#### Result 3.	Few species contain reach DRI targets for multiple nutrients. 

Now let's find out how many species reach more than one mineral RDI target
```{r}

## sidebar: let's take aq.long and turn it into wide format

aq.wide <- spread(n.long, nutrient, concentration)
aq.wide$species <- as.factor(aq.wide$species)
write.csv(aq.wide, "/Users/Joey/Documents/Nutrient_Analysis/data/aq.wide.csv")
aq.wide <- read.csv("/Users/Joey/Documents/Nutrient_Analysis/data/aq.wide.csv")


aq.wide$species <- as.factor(aq.wide$species)

sp.subgroup <- aq.wide %>%
  group_by(species) %>% 
  select(Subgroup, species) %>% 
  distinct(species)

length(is.na(aq.wide$CA_mg))

ntbl.RDI.tot <- minerals %>% 
  group_by(species) %>% 
  summarise(mean.CA = mean(CA_mg, na.rm = TRUE),
            mean.ZN = mean(ZN_mg, na.rm = TRUE), 
            mean.FE = mean(FE_mg, na.rm = TRUE)) %>% 
  mutate(RDI.CA = ifelse(mean.CA > 300, 1, 0)) %>% 
  mutate(RDI.FE = ifelse(mean.FE > 4.5, 1, 0)) %>% 
  mutate(RDI.ZN = ifelse(mean.ZN > 2.75, 1, 0)) %>%
  mutate(RDI.micro.tot = rowSums(.[5:7])) %>% 
  filter(!is.na(RDI.micro.tot)) %>% 
  arrange(., RDI.micro.tot) 

ntbl.RDI.tot.10 <- minerals %>% 
  group_by(species) %>% 
  summarise(mean.CA = mean(CA_mg, na.rm = TRUE),
            mean.ZN = mean(ZN_mg, na.rm = TRUE), 
            mean.FE = mean(FE_mg, na.rm = TRUE)) %>% 
  mutate(RDI.CA = ifelse(mean.CA > 120, 1, 0)) %>% 
  mutate(RDI.FE = ifelse(mean.FE > 1.8, 1, 0)) %>% 
  mutate(RDI.ZN = ifelse(mean.ZN > 1.1, 1, 0)) %>%
  mutate(RDI.micro.tot = rowSums(.[5:7])) %>% 
  filter(!is.na(RDI.micro.tot)) %>% 
  arrange(., RDI.micro.tot)


# ##now the same thing, but using the aq.wide
# 
# aq.wide.CA <- aq.wide %>% 
#   group_by(species) %>% 
#   summarise(mean.CA = mean(CA_mg, na.rm = TRUE))
# 
# hist(aq.wide.CA$mean.CA)
#   


ntbl.RDI.tot.aq <- aq.wide %>% 
  group_by(species) %>% 
  summarise(mean.CA = mean(CA_mg, na.rm = TRUE),
            mean.ZN = mean(ZN_mg, na.rm = TRUE), 
            mean.FE = mean(FE_mg, na.rm = TRUE)) %>%
  mutate(RDI.CA = ifelse(mean.CA > 120, 1, 0)) %>% 
  mutate(RDI.FE = ifelse(mean.FE > 1.8, 1, 0)) %>% 
  mutate(RDI.ZN = ifelse(mean.ZN > 1.1, 1, 0)) %>%
  mutate(RDI.micro.tot = rowSums(.[5:7])) %>% 
  filter(!is.na(RDI.micro.tot)) %>% 
  arrange(., RDI.micro.tot) 

table(ntbl.RDI.tot$RDI.micro.tot)


### first, get the subgroup column back into the RDI matrix
ntbl.RDI.sub <- inner_join(ntbl.RDI.tot, ntbl.raw, by = "species")
ntbl.RDI.sub10 <- inner_join(ntbl.RDI.tot.10, ntbl.raw, by = "species")
ntbl.RDI.subaq <- inner_join(ntbl.RDI.tot.aq, aq.wide, by = "species")


ntbl.RDI.sub4 <- dplyr::left_join(ntbl.RDI.tot, ntbl.raw, by = "species") 

ntbl.RDI.sub %>% 
  group_by(Subgroup, RDI.micro.tot) %>% 
  summarise(n = n()) %>% 
  mutate(cum.RDI = cumsum(n)) %>% 
  ggplot(., aes(x = RDI.micro.tot, y = cum.RDI)) + geom_bar(stat = "identity") + facet_wrap(~ Subgroup, scales = "free_y")  


qplot(factor(Subgroup), data = ntbl.RDI.sub10, geom = "bar", fill = factor(RDI.micro.tot)) + theme_bw()
ggsave("/Users/Joey/Documents/Nutrient_Analysis/figures/RDI.stacked.barchart.png")
ggplot(ntbl.RDI.subaq, aes(RDI.micro.tot)) + geom_bar(binwidth = .5) + facet_wrap(~ Subgroup, scales = "free_y")  
ggsave("/Users/Joey/Documents/Nutrient_Analysis/figures/RDI.targets.barchart.png")

### What percentage of each groups reaches at least one RDI target?

ntbl.RDI.sub %>% 
  dplyr::filter(Subgroup == "Molluscs") %>% 
  # distinct(species) %>% 
  dplyr::filter(RDI.micro.tot > 0) %>% 
  dplyr::distinct(species) %>% 
  count()
  
  table(ntbl.RDI.sub$Subgroup)


  
  
### eight out of 10 Molluscs reach at least one RDI target, 21 out of 80 finfish reach at least one RDI target, 3 out of 7 crustacean species reach at least one RDI target. 

  ntbl.RDI.tot <- minerals %>% 
  group_by(species) %>% 
  summarise(mean.CA = mean(CA_mg, na.rm = TRUE),
            mean.ZN = mean(ZN_mg, na.rm = TRUE), 
            mean.FE = mean(FE_mg, na.rm = TRUE)) %>% 
  mutate(RDI.CA = ifelse(mean.CA > 300, 1, 0)) %>% 
  mutate(RDI.FE = ifelse(mean.FE > 4.5, 1, 0)) %>% 
  mutate(RDI.ZN = ifelse(mean.ZN > 2.75, 1, 0)) %>%
  mutate(RDI.micro.tot = rowSums(.[5:7])) %>% 
  filter(!is.na(RDI.micro.tot)) %>% 
  arrange(., RDI.micro.tot) 





RDI.freq <- read.csv("/Users/Joey/Documents/Nutrient_Analysis/data/RDI.freq.csv")
RDI.freq <- read.csv("~/Documents/Nutrient_Analysis/data/RDI.freq.csv")
str(RDI.freq)


ggplot(subset(RDI.freq, target == "25 percent"), aes(x = reorder(number_targets, -frequency), y = frequency)) +  geom_bar(stat = "identity", width = 0.5) + xlab("number of 25% RDI targets reached") + theme(axis.text=element_text(size=14),
        axis.title=element_text(size=14,face="bold"))
ggsave("/Users/Joey/Documents/Nutrient_Analysis/figures/RDI.25-targets-barchart.png")


#' for the 25% RDI targets, for the 106 species for which we have data for all 3 minerals, 65 spp reach 0 targets, 30 reach 1 target, 9 reach 2 targets, and 2 reach all 3 targets. In other words, 41 reach 1 or more targets, 39 reach two or more targets and 2 reach all three targets.  
#' for the 10% RDI targets,  56 reach 0 targets, 9 reach 1 target, 26 reach 2 targets and 15 reach all 3 targets. Or, in other words, 50 reach one or more targets, 41 reach 2 or more targets, and 15 reach all three targets. 
```

#### How many species reach RDI, for each nutrient invidually?

```{r}
n.long <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/ntbl.long.csv")
n.long <- n.long %>% 
  group_by(Subgroup) %>% 
  mutate(RDI.25per = (concentration > (RDI/4)),
         RDI.per = (concentration/RDI),
         RDI.20per = (concentration/(RDI/5)),
         RDI.15per = (concentration/(RDI/6)),
         RDI.target = (concentration > (RDI/10)))

n.long.RDI <- n.long %>% 
  filter(!is.na(RDI.25per))
## try to make bar chart with number of RDI hits, grouped by Subgroup
qplot(factor(Subgroup), data = n.long.RDI, geom = "bar", fill = factor(RDI.25per))




# RDI.prop <- lm(log(mean.RDI) ~ log(max_size), data = n.long)
# summary(RDI.prop)
# confint(RDI.prop)
# visreg::visreg(RDI.prop, xtrans = log)
```
body.prop: If max size is less than 100g, gets whole, if not, gets part. bones.body is a combo of fish less than 100g and those from Cambodia where study noted that bones were eaten.
```{r}
n.long <- n.long %>% 
  mutate(body.whole = (max_size < 0.1),
         eat.bones = (Abs_lat == 12.265754 | Abs_lat == 11.066667),
         bones.body = (max_size < 0.1 | Abs_lat == 12.265754 | Abs_lat == 11.066667),
         bones.body.invert = (max_size < 0.1 | Abs_lat == 12.265754 | Abs_lat == 11.066667 | Subgroup != "Finfish"))


### this code gets me the results of what percentage of observations reach 10% RDI for whole body or just part
n.long %>% 
  # filter(nutrient == "CA_mg") %>% 
  dplyr::select(nutrient, RDI.target, bones.body) %>% 
  table()

table <- n.long %>% 
  # filter(nutrient == "CA_mg") %>% 
  dplyr::select(RDI.target, bones.body) %>% 
  table()

mosaicplot(table)

n.long %>% 
  filter(nutrient == "PROTEIN",
         bones.body.invert == FALSE) %>% 
  dplyr::select(RDI.target) %>% 
table()
```

```{r}
n.long %>% 
  filter(!is.na(bones.body)) %>% 
  # arrange(desc(nutrient)) %>% 
  ggplot(., aes(x = nutrient, y = log(RDI.per), fill = bones.body, geom = "boxplot")) +
 geom_boxplot() +
  theme_minimal() +
  geom_hline(yintercept=log(.10)) +
  ylab("percentage of RDI in edible portion, log scale")
ggsave("/Users/Joey/Documents/Nutrient_Analysis/figures/bones.body-RDI.png")
```


####Result 4. Few species reach DRI for multiple nutrients.

How many species reach RDI for each nutrient?
10% RDI: calcium: 28/99, zinc: 39/101, iron: 23/104, EPA: 117/238, DHA: 168/235, Fat: 47/277, Protein: 251/251  
```{r}
n.long <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/ntbl.long.csv", col_names = TRUE, na = c("", "NA"))
str(n.long)

## arrgh, I couldn't figure out the arguments to read_csv, so I'm converting to factor here:
n.long$species <- as.factor(n.long$species)
n.long$nutrient <- as.factor(n.long$nutrient)
n.long$Subgroup <- as.factor(n.long$Subgroup)


n.long %>% 
  filter(nutrient == "PROTEIN") %>% 
  filter(!is.na(concentration)) %>% 
  distinct(species) %>% 
  count()

n.long %>% 
  filter(nutrient == "PROTEIN") %>%
  mutate(RDI.10 = (concentration > (RDI/10))) %>% 
    filter(RDI.10 == "TRUE") %>% 
  distinct(species) %>%
  count()
```

#### Result 5. Within functional groups, some traits such body size and latitude are strongly associated with nutritional profile ####

```{r}
fb.all <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/fb.all.csv")
fb.length <- fb.all %>% 
   dplyr::select(species, CA_mg, ZN_mg, FE_mg, EPA_g, DHA_g, Length, max_length, Subgroup, Habitat, TL, FoodTroph.x, Herbivory2, Abs_lat, DemersPelag, taxon, max_size) %>% 
  rename(FoodTroph = FoodTroph.x) %>% 
  mutate(species = as.factor(species))

table(fb.length$Subgroup)

ZN.all <- standardize(lm(log(ZN_mg) ~ log(Length) + TL + Habitat + Abs_lat, data = fb.length, na.action = "na.omit"))
test.ZN.all <- tidy(ZN.all, conf.int =TRUE)
summary(ZN.all)


test.ZN.all$term <- factor(test.ZN.all$term, levels=unique(test.ZN.all$term))
ggplot(test.ZN.all, aes(x=term, y=estimate, ymin=conf.low, ymax=conf.high)) +
  geom_pointrange() + 
  coord_flip() + 
  geom_hline(aes(x=0), lty=2) +
  xlab('term ZN') +
  ylab('Regression Coefficient') + theme(legend.position="none")

CA.all <- standardize(lm(log(CA_mg) ~ log(max_size) + TL + Habitat + Abs_lat, data = fb.length, na.action = "na.omit"))
test.CA.all <- tidy(CA.all, conf.int =TRUE) 

test.CA.all$term <- factor(test.CA.all$term, levels=unique(test.CA.all$term))
ggplot(test.CA.all, aes(x=term, y=estimate, ymin=conf.low, ymax=conf.high)) +
  geom_pointrange() + 
  coord_flip() + 
  geom_hline(aes(x=0), lty=2) +
  xlab('term CA') +
  ylab('Regression Coefficient') + theme(legend.position="none")
coefplot(CA.all, innerCI = 2, intercept = FALSE)

ZN.all <- standardize(lm(log(ZN_mg) ~ log(Length) + TL + Habitat + Abs_lat, data = fb.length, na.action = "na.omit"))
test.ZN.all <- tidy(ZN.all, conf.int =TRUE) 

CA.all <- standardize(lm(log(CA_mg) ~ log(Length) + TL + Habitat + Abs_lat, data = fb.length, na.action = "na.omit"))
test.CA.all <- tidy(CA.all, conf.int =TRUE)

FE.all <- standardize(lm(log(FE_mg) ~ log(Length) + TL + Habitat + Abs_lat, data = fb.length, na.action = "na.omit"))
test.FE.all <- tidy(FE.all, conf.int =TRUE) 

EPA.all <- standardize(lm(log(EPA_g) ~ log(Length) + TL + Habitat + Abs_lat, data = fb.length, na.action = "na.omit"))
test.EPA.all <- tidy(EPA.all, conf.int =TRUE)

DHA.all <- standardize(lm(log(DHA_g) ~ log(Length) + TL + Habitat + Abs_lat, data = fb.length, na.action = "na.omit"))
test.DHA.all <- tidy(DHA.all, conf.int =TRUE) 

multiplot(ZN.all, CA.all, FE.all, EPA.all, DHA.all, innerCI = 2, intercept = FALSE)
ggsave("/Users/Joey/Documents/Nutrient_Analysis/figures/coefplot.png")
```

Inverts traits
```{r}
intbl <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/intbl.all.csv")
intbl <- intbl %>% 
  mutate(Subgroup = as.factor(Subgroup),
         DemersPelag = as.factor(DemersPelag),
         taxon = as.factor(taxon),
         Habitat = as.factor(Habitat))

table(intbl$DemersPelag)
hist(intbl$Weight)

class(intbl$Weight)
summary(intbl$FoodTroph)

intbl$Weight <- as.numeric(intbl$Weight)

inv.length <- lm(log(CA_mg) ~ log(Length) + FoodTroph, data = intbl)
inv.size <- lm(log(CA_mg) ~ log(Length), data = intbl)
summary(inv.length)
summary(inv.size)
confint(inv.size)
coefplot::coefplot(inv.length, innerCI = 2, intercept = FALSE)
length(!is.na(intbl$taxon))

### merge the inverts and verts
fb <- fb.all %>% 
   dplyr::select(species, CA_mg, ZN_mg, FE_mg, EPA_g, DHA_g, Length, max_length, Subgroup, Habitat, TL, FoodTroph.x, Herbivory2, Abs_lat, DemersPelag, taxon, max_size, Weight) %>% 
  rename(FoodTroph = FoodTroph.x) %>% 
  mutate(species = as.factor(species))
sb <- intbl %>% 
   dplyr::select(species, CA_mg, ZN_mg, FE_mg, EPA_g, DHA_g, Length, max_length, Subgroup, Habitat, TL, FoodTroph, Herbivory2, Abs_lat, DemersPelag, taxon, max_size, Weight) %>% 
  mutate(species = as.factor(species))

ntbl <- bind_rows(fb, sb)
write.csv(ntbl, "/Users/Joey/Documents/Nutrient_Analysis/data/ntbl.int.csv")

class(ntbl$FoodTroph)
ntbl <- ntbl %>% 
  mutate(Subgroup = as.factor(Subgroup),
         DemersPelag = as.factor(DemersPelag),
         taxon = as.factor(taxon),
         Habitat = as.factor(Habitat))

ntbl.CA <- ntbl %>% 
  filter(!is.na(CA_mg))
#          !is.na(max_size),
#          # !is.na(Abs_lat),
#          !is.na(Subgroup),
#          # !is.na(taxon),
#          # !is.na(Habitat),
#          # !is.na(DemersPelag))

ntbl.CA$Subgroup <- droplevels(ntbl.CA$Subgroup)

library(gdata)

ntbl.CA <- ntbl.CA %>% 
  mutate(Subgroup = droplevels(Subgroup),
         Habitat = droplevels(Habitat),
         DemersPelag = droplevels(DemersPelag),
         taxon = droplevels(taxon))
str(ntbl.CA)

ntbl.CA <- drop.levels(ntbl.CA)
table(ntbl.CA$Subgroup)

mod1 <- lm(log(CA_mg) ~ log(max_size) + FoodTroph + Subgroup + taxon + Habitat + Abs_lat, data = ntbl)
summary(mod1)

mod1s <- standardize(lm(log(CA_mg) ~ log(max_size) + FoodTroph + taxon + Habitat + Abs_lat, na.action = na.omit, data = ntbl))
coefplot(mod1s, innerCI = 2, intercept = FALSE)
summary(mod1s)
confint(mod1s)
summary(ntbl.CA$Abs_lat)



mod2 <- lm(log(CA_mg) ~ log(Length) + FoodTroph + Habitat + Abs_lat + Subgroup, data = ntbl)
# mod2 <- standardize(lm(log(CA_mg) ~ log(max_size) + FoodTroph + Habitat + Abs_lat + Subgroup, data = ntbl))
# mod1 <- standardize(lm(log(CA_mg) ~ log(max_size) + FoodTroph + Subgroup + DemersPelag + taxon + Habitat + Abs_lat, data = ntbl.CA))
# mod1.tidy <- tidy(mod1, conf.int = TRUE)
summary(mod2)
coefs <- buildModelCI(mod1) 
confint(mod2)

mod2 <- lm(log(CA_mg) ~ log(Weight), data = ntbl)
coefplot(mod2, innerCI = 2, intercept = FALSE)
ggsave("/Users/Joey/Documents/Nutrient_Analysis/figures/CA_length_coefplot.png")

modZN <- lm(log(ZN_mg) ~ log(max_size) + FoodTroph + Habitat + Abs_lat, data = ntbl)
summary(modZN)
confint(modZN)

modFE <- lm(log(FE_mg) ~ log(max_size) + FoodTroph + Habitat + Abs_lat, data = ntbl)
summary(modFE)
confint(modFE)


length(unique(ntbl$Weight))
visreg::visreg(mod2, xtrans = log)
hist(ntbl$Weight)

```

#### Result 6.	Functional group diversity enhances dietary nutritional diversity and nutritional benefits that human communities may derive from seafood assemblages. (nutrient accumulation curve). 

#####How important is functional diversity?

Here we look at the three minerals. 
```{r}
ntbl.raw <- read.csv("/Users/Joey/Documents/Nutrient_Analysis/data/ntbl2.csv")
inverts.new <- read_csv("/Users/Joey/Documents/Nutrient_Analysis/data/aquatic_inverts_micronutrients.csv")

#create a df that is just the minerals and the species info
ntbl.minerals <- ntbl.raw %>% 
  dplyr::select(Subgroup, species, CA_mg, FE_mg, ZN_mg)


inverts.minerals <- inverts.new %>% 
  dplyr::select(Subgroup, species, CA_mg, FE_mg, ZN_mg)
  # filter(Subgroup != "Echinoderm") 

#join the new old ntbl data with the new inverts mineral data
minerals <- bind_rows(ntbl.minerals, inverts.minerals)
```


#### SAC
```{r}
#step 1. create a matrix with just 0 and 1 for whether a given species reaches RDI
ntbl.RDI <- minerals %>% 
  group_by(species) %>% 
  summarise(mean.CA = mean(CA_mg, na.rm = TRUE),
            mean.ZN = mean(ZN_mg, na.rm = TRUE), 
            mean.FE = mean(FE_mg, na.rm = TRUE)) %>% 
  mutate(RDI.CA = ifelse(mean.CA > 300, 1, 0)) %>% 
  mutate(RDI.FE = ifelse(mean.FE > 4.5, 1, 0)) %>% 
  mutate(RDI.ZN = ifelse(mean.ZN > 2.75, 1, 0)) %>%
  mutate(RDI.micro.tot = rowSums(.[5:7])) %>% 
  filter(!is.na(RDI.micro.tot)) %>% 
  # arrange(., RDI.micro.tot) %>% 
  # select(., c(1,5:7))
  dplyr::select(., 5:7)

#step 2. create the same matrix, but this time remove the molluscs
ntbl.RDI.noMoll <- minerals %>% 
  group_by(species) %>% 
  filter(Subgroup != "Molluscs") %>% 
  summarise(mean.CA = mean(CA_mg, na.rm = TRUE),
            mean.ZN = mean(ZN_mg, na.rm = TRUE), 
            mean.FE = mean(FE_mg, na.rm = TRUE)) %>% 
  mutate(RDI.CA = ifelse(mean.CA > 300, 1, 0)) %>% 
  mutate(RDI.FE = ifelse(mean.FE > 4.5, 1, 0)) %>% 
  mutate(RDI.ZN = ifelse(mean.ZN > 2.75, 1, 0)) %>%
  mutate(RDI.micro.tot = rowSums(.[5:7])) %>% 
  filter(!is.na(RDI.micro.tot)) %>% 
  # arrange(., RDI.micro.tot) %>% 
  # select(., c(1,5:7))
  dplyr::select(., 5:7)
```

#####Create the species/nutrient accumulation curve
```{r}
spa.rand <- specaccum(ntbl.RDI, method = "random")
# png(filename = "sac.full.vs.noMoll.png", width = 6, height = 4, units = 'in', res = 300)
spa.rand$sites
plot(spa.rand, col = "cadetblue", lwd = 2, ci = 1, ci.type = "bar", ci.lty = 3,  ci.col = "cadetblue", ylim = c(0,4), xlim = c(0,80), xlab = "number of fish species in diet", ylab = "number of distinct RDI targets reached", main = "25% RDI targets")
abline( v= 15, col = "cadetblue")
abline( v = 26, col = "pink")
# dev.off()
summary(spa.rand)

#Now create the analagous curve for the no mollusc dataset, and plot both curves on the same axis (question to self...is it a fair comparison to compare against the full dataset? should I also remove the same amount of finfish from the full dataset to make a fair comparison?)

# png(filename = "/Users/Joey/Documents/Nutrient_Analysis/figures/sac.full.vs.noMoll.png", width = 10, height = 8, units = 'in', res = 300)
spa.rand.noMoll <- specaccum(ntbl.RDI.noMoll, method = "random")
plot(spa.rand, col = "black", lwd = 4, ci = 1, ci.type = "bar", ci.lty = 3,  ci.col = "blue", ylim = c(0,3.5), xlim = c(0,60), xlab = "number of fish species in diet", ylab = "number of distinct RDI targets reached", main = "micronutrients: 25% RDI targets")
plot(spa.rand.noMoll, add = TRUE, col = "darkgrey", lwd = 4, ci = 1, ci.type = "bar", ci.lty = 3,  ci.col = "darkgrey", ylim = c(0,3.5), xlim = c(0,60), xlab = "number of fish species in diet", ylab = "number of distinct RDI targets reached", main = "25% RDI targets")
# dev.off()
legend('bottomright', legend = c("full", "no molluscs"), lty=c(1,1), lwd=c(4.4), col=c('black', 'darkgrey')) # gives the legend lines the correct color and width))

summary(spa.rand.noMoll)

## Results from random nutrient accumulation:
## Need to sample from 14 species to get a median of all three minerals without molluscs, and need to sample from 8 species to get a median of 3 minerals when molluscs are included. 
```

#### All micronutrients accumulation ####
Now repeat the same process, but now include the three minerals plus the two fatty acids.
```{r}
ntbl.micronuts <- ntbl.raw %>% 
  dplyr::select(Subgroup, species, CA_mg, FE_mg, ZN_mg, EPA_g, DHA_g)

#step 1. create a matrix with just 0 and 1 for whether a given species reaches RDI
ntbl.RDI.all <- ntbl.micronuts %>% 
  group_by(species) %>% 
  summarise(mean.CA = mean(CA_mg, na.rm = TRUE),
            mean.ZN = mean(ZN_mg, na.rm = TRUE), 
            mean.FE = mean(FE_mg, na.rm = TRUE),
            mean.EPA = mean(EPA_g, na.rm = TRUE),
            mean.DHA = mean(DHA_g, na.rm = TRUE)) %>% 
  mutate(RDI.CA = ifelse(mean.CA > 300, 1, 0)) %>% 
  mutate(RDI.FE = ifelse(mean.FE > 4.5, 1, 0)) %>% 
  mutate(RDI.ZN = ifelse(mean.ZN > 2.75, 1, 0)) %>%
  mutate(RDI.EPA = ifelse(mean.EPA > 0.25, 1, 0)) %>% 
  mutate(RDI.DHA = ifelse(mean.DHA > 0.25, 1, 0)) %>% 
  mutate(RDI.micro.tot = rowSums(.[7:11])) %>% 
  filter(!is.na(RDI.micro.tot)) %>% 
  # arrange(., RDI.micro.tot) %>% 
  # dplyr::select(., c(1,5:7))
  dplyr::select(., 7:11)

ntbl.RDI.all.noMoll <- ntbl.micronuts %>% 
  group_by(species) %>% 
  filter(Subgroup != "Molluscs") %>% 
  summarise(mean.CA = mean(CA_mg, na.rm = TRUE),
            mean.ZN = mean(ZN_mg, na.rm = TRUE), 
            mean.FE = mean(FE_mg, na.rm = TRUE),
            mean.EPA = mean(EPA_g, na.rm = TRUE),
            mean.DHA = mean(DHA_g, na.rm = TRUE)) %>% 
  mutate(RDI.CA = ifelse(mean.CA > 300, 1, 0)) %>% 
  mutate(RDI.FE = ifelse(mean.FE > 4.5, 1, 0)) %>% 
  mutate(RDI.ZN = ifelse(mean.ZN > 2.75, 1, 0)) %>%
  mutate(RDI.EPA = ifelse(mean.EPA > 0.25, 1, 0)) %>% 
  mutate(RDI.DHA = ifelse(mean.DHA > 0.25, 1, 0)) %>% 
  mutate(RDI.micro.tot = rowSums(.[7:11])) %>% 
  filter(!is.na(RDI.micro.tot)) %>% 
  # arrange(., RDI.micro.tot) %>% 
  # dplyr::select(., c(1,5:7))
  dplyr::select(., 7:11)

## Create the sac

spa.rand.all <- specaccum(ntbl.RDI.all, method = "random")
spa.rand.all.noMoll <- specaccum(ntbl.RDI.all.noMoll, method = "random")
# png(filename = "sac.full.vs.noMoll.png", width = 6, height = 4, units = 'in', res = 300)
plot(spa.rand.all, col = "cadetblue", lwd = 4, ci = 1, ci.type = "bar", ci.lty = 3,  ci.col = "cadetblue", ylim = c(0,6), xlim = c(0,80), xlab = "number of fish species in diet", ylab = "number of distinct RDI targets reached", main = "25% RDI targets")
plot(spa.rand.all.noMoll, add = TRUE, col = "darkgrey", lwd = 4, ci = 1, ci.type = "bar", ci.lty = 3,  ci.col = "darkgrey", ylim = c(0,6), xlim = c(0,60), xlab = "number of fish species in diet", ylab = "number of distinct RDI targets reached", main = "25% RDI targets")
summary(spa.rand.all)

summary(spa.rand.all.noMoll)


### Result, need to sample from 15 species to reach a median of all 5 micronutrient targets (when molluscs are included), need to sample from 22 species when molluscs are excluded. 
```


